Modelling temporal dependence and multilevel structure using hidden Markov models

### 2020-07-22 Report/Sections/discussion.tex

An example of balancing model complexity with efficient fitting is presented in our simulation study. Sub-dive behavioral states were shared across dive types to reduce model complexity, and by far the fastest model to train ($\approx$ 15 minutes) was the CarHMM-DFT, which had no hierarchical component. Even still, the CarHMM-DFT had near-perfect accuracy when decoding sub-dive behavioral states of the simulated whale.
However, this model is not sufficient if ecologists wish to understand to joint relationship between dive type and intra-dive behaviour.

>>>>

An example of balancing model complexity with efficient fitting is presented in our simulation study. Sub-dive behavioral states were shared across dive types to reduce model complexity, and by far the fastest model to train was the CarHMM-DFT, which had no hierarchical component. Even still, the CarHMM-DFT had near-perfect accuracy when decoding sub-dive behavioral states of the simulated whale.
However, this model is not sufficient if ecologists wish to understand to joint relationship between dive type and intra-dive behaviour.
